A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-19 paper.tex
add . into two places of section 1

Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility this has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

@@

\item The {\bf granularity} of the dependencies may not be well understood.
For example, the user may understand that a computation depends upon
a data collection that is 1TB in overall size, but not have detailed
knowledge that it only requires three files totalling 300MB out of that
whole collection

@@

The application which is the study of this paper is called \emph{TauRoast}
It searches for cases where the Higgs boson decays to two tau leptons.
The leptons are not observed directly, but by the particle showers
that they generate.  So, the analysis must search for detector
events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
the events of interest (Higgs decays) from all other events and
are also used in further statistical analysis.

>>>>

Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

@@

\item The {\bf granularity} of the dependencies may not be well understood.
For example, the user may understand that a computation depends upon
a data collection that is 1TB in overall size, but not have detailed
knowledge that it only requires three files totalling 300MB out of that
whole collection.

@@

The application which is the study of this paper is called \emph{TauRoast}.
It searches for cases where the Higgs boson decays to two tau leptons.
The leptons are not observed directly, but by the particle showers
that they generate.  So, the analysis must search for detector
events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
the events of interest (Higgs decays) from all other events and
are also used in further statistical analysis.
